---
title: "Analysis of Some Aspects of Gameplay of *Pandemic*"
author: |
  | Marcelo Ventura Freire
  | Rafael Ozzetti
  | Tiago Tomazi
date: "`r format(Sys.time(), '%Y-%b-%d')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    number_sections: yes
  html_document:
    number_sections: yes
    smart: yes
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(igraph)
library(tidyverse)
library(tidygraph)
library(ggrepel)
library(ggraph)
```

# Introducion 

## The Game *Pandemic*

## Basic Gameplay, its 7 variants, and its 5 expansions

### How to make a competition out of a cooperative game

### *Pandemic Survival*

## Concepts

### Cooperative Game

### Cities and the Map

### Deseases and Cures

### Infections, Epidemies, and Outbreaks

### Movement and Spacial Actions

### Specialist Characters

## Game Dynamics

### Desease Spread in the Map

### Infection Deck and Players' Deck

### Turn Structure

### Game Progress Indicators

# Graph Theory's Aspects

## Nodes and Edges

```{r read.graph}
nodes <- 
  read.csv("nodes.csv", strip.white = T, stringsAsFactors = F) %>%
  mutate(
    id = 1:n(), 
    contagion = 0
  )
adjacency <- 
  read.csv("adjacency.csv", header = F) %>% 
  as.matrix() %>%
  set_colnames(nodes$name) %>%
  set_rownames(nodes$name)
print(adjacency)
world <- 
  adjacency %>%
  as_tbl_graph(directed = F) %>%
  activate(nodes) %>%
  left_join(nodes, by = "name") 
print(world)
world %>% 
  as_edgelist() %>% 
  as.tibble() %>% 
  set_colnames(c("from", "to")) %>%
  # write_csv("edgelist.csv")
  print()
```

```{r plot.graph}
plot.graph <- 
  function(layout, ...) {
    ggraph(world, layout = layout, ...) +
      geom_node_label(aes(label = name, colour = color)) + 
      geom_edge_link() +
      ggtitle(layout) +
      theme_void()
  }
plot.graph("nicely")
plot.graph("mds")
plot.graph("sphere")
plot.graph("kk")
plot.graph("drl")
plot.graph("lgl")
plot.graph("circle")
plot.graph("linear", circular = T)
```
## Adjacency Matrix to the cities

```{r adjacency}
print(adjacency)
```

## Distance Matrix between the cities

Calculating the matrix

```{r distance}
A <- adjacency
dimnames(A) <-NULL
B <- diag(1, nrow(adjacency))
distances <- adjacencies <- list()
k <- 0
repeat {
  distances[[k+1]] <- ifelse(B > 0, k, Inf)
  adjacencies[[k+1]] <- B
  if (all(B > 0))
    break
  k <- k + 1
  B <- B %*% A
}
distance <- 
  do.call(pmin, distances) %>%
  set_colnames(nodes$name) %>%
  set_rownames(nodes$name)
# print(distance)
# write.csv(distance, "distance.csv")
```

Incorporating a 3D Multidimensional Scaling of the distance matrix in the network

```{r mds.distance}
world %<>%
  activate(nodes) %>%
  left_join(
    cmdscale(distance, k = 3) %>% 
      as.data.frame() %>%
      rownames_to_column() %>%
      set_colnames(c("name", "x", "y", "z")),
    by = "name"
  ) 
print(world)
```


```{r plot.graph.3d}
# rglplot(world, dim = 3)
```



## Where to build centers

```{r build.centers}
centers <- c("Atlanta") # initial center
```

### Where to build centers given the most probable cities with initial infection


# Probability and Decision Theories' Aspects

## Basic Gameplay *versus* Championship

## Basic Gameplay: Restricted Shuffling 

## Championship: Partial Deck Building and Restricted Shuffling 

# All together now: Graph, Probability and Decision Theories 

## The cities that will have infection

## The maximum number of cities that will be infected

## Maximum distance among infected cities

## When it is worth to build center

## How many centers to build

## Where to build centers




