---
title: "Analysis of Some Aspects of Gameplay of *Pandemic*"
author: |
        | Marcelo Ventura Freire
        | Thiago Tomazi
date: "`r format(Sys.time(), '%Y-%b-%d')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    smart: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

# Introducion 

## The Game *Pandemic*

## Basic Gameplay, its 7 variants, and its 5 expansions

### How to make a competition out of a cooperative game

### *Pandemic Survival*

## Concepts

### Cooperative Game

### Cities and the Map

### Deseases and Cures

### Infections, Epidemies, and Outbreaks

### Movement and Spacial Actions

### Specialist Characters

## Game Dynamics

### Desease Spread in the Map

### Infection Deck and Players' Deck

### Turn Structure

### Game Progress Indicators

# Graph Theory's Aspects

## Nodes and Edges

```{r}
nodes <- read.csv("nodes.csv", strip.white = T)
centers <- nodes$name[c(1)]
adjacency <- 
  read.csv("adjacency.csv", header = F) %>% 
  as.matrix() %>%
  `dimnames<-`(list(nodes$name, nodes$name))

# edges <- ???

```



## Adjacency Matrix to the cities

## Distance Matrix between the cities

# Probability and Decision Theories' Aspects

## Basic Gameplay *versus* Championship

## Basic Gameplay: Restricted Shuffling 

## Championship: Partial Deck Building and Restricted Shuffling 



