---
title: "Analysis of Some Aspects of Gameplay of *Pandemic*"
author: |
        | Marcelo Ventura Freire
        | Thiago Tomazi
date: "`r format(Sys.time(), '%Y-%b-%d')`"
output: 
 html_document:
   toc: true
   toc_depth: 2
   number_sections: true
   smart: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

# Introducion 

## The Game *Pandemic*

## Basic Gameplay, its 7 variants, and its 5 expansions

### How to make a competition out of a cooperative game

### *Pandemic Survival*

## Concepts

### Cooperative Game

### Cities and the Map

### Deseases and Cures

### Infections, Epidemies, and Outbreaks

### Movement Actions

### Special Actions

### Specialist Characters

## Game Dynamics

### Desease Spread in the Map

### Infection Deck and Players' Deck

### Turn Structure

### Game Progress Indicators

# Graph Theory's Aspects

## Nodes and Edges

```{r}
"
city, color
Atlanta, blue
Chicago, blue
Essen, blue
London, blue
Madrid, blue
Milan, blue
Montreal, blue
NewYork, blue
Paris, blue
SanFrancisco, blue
StPetersburg, blue
Washington, blue
Algiers, black
Baghdad, black
Cairo, black
Chennai, black
Delhi, black
Istanbul, black
Karachi, black
Kolkata, black
Moscow, black
Mumbai, black
Riyadh, black
Tehran, black
Bogota, yellow
BuenosAires, yellow
Johannesburg, yellow
Khartoum, yellow
Kinshasa, yellow
Lagos, yellow
Lima, yellow
LosAngeles, yellow
MexicoCity, yellow
Miami, yellow
Santiago, yellow
SaoPaulo, yellow
Bangkok, red
Beijing, red
HoChiMinh, red
HongKong, red
Jakarta, red
Manila, red
Osaka, red
Seoul, red
Shanghai, red
Sydney, red
Taipei, red
Tokyo, red
" %>%
  read.csv(text = .) -> nodes
```



## Adjacency Matrix to the cities

## Distance Matrix between the cities

# Probability and Decision Theories' Aspects

## Basic Gameplay *versus* Championship

## Basic Gameplay: Restricted Shuffling 

## Championship: Partial Deck Building and Restricted Shuffling 



